Binary companions of red giant stars in \apogee\ \DR: \\ Search method and catalog of $>$4,500 systems

### 2018-03-20 paper/1-catalog/twoface-catalog.tex
Figure

Here we highlight a few interesting results from visualizing the properties of
companions in the unimodal and bimodal samples defined above (see \sectionname
s~\ref{sec:catalog-unimodal} and \ref{sec:catalog-multimodal}).
In all figures, we only plot companions with inferred orbits that pass our
visual inspection (\texttt{clean\_flag == 0}).
We additionally restrict to stars with $\logg > 2$ to avoid upper RGB stars
that may have coherent oscillations that mimic RV modulations from companions.

\todo{here:} \figurename~\ref{fig:logg-teff-p} ...

% Notebook: "Results"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{mass}
\end{center}
\caption{%
\textit{Left panel:}
\textit{Right panel:}
\label{fig:logg-teff-p}
}
\end{figure}

@@

Most of the companions we find have minimum masses $M_{2, \textrm{min}} <
1~\msun$.
\figurename~\ref{fig:mass}, left panel shows primary and companion mass
estimates for systems with unimodal (black markers) and bimodal (blue lines)
period samplings for the subset of /\nunimodal\ unimodal and /\nbimodal\ bimodal
systems with primary mass estimates, again using primary masses from
\citet{Ness:2015}.
Upper dashed line shows the $M_{2, \textrm{min}} = M_1$ curve, and lower dashed
line shows the Hydrogen-burning limit, $M_{2, \textrm{min}} = 0.08~\msun$.
For the systems with bimodal samplings, we compute the minimum companion mass
for each period mode and connect these estimates with a line.

>>>>

Here we highlight a few interesting results from visualizing the properties of
companions in the unimodal and bimodal samples defined above (see \sectionname
s~\ref{sec:catalog-unimodal} and \ref{sec:catalog-multimodal}).
In all figures, we only plot companions with inferred orbits that pass our
visual inspection (\texttt{clean\_flag == 0}).

\todo{here:} \figurename~\ref{fig:logg-teff-p-e} ...

% Notebook: "Results"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{P-Teff-logg-e}
\end{center}
\caption{%
\textit{Top:} Inferred orbital period and eccentricity for all systems with unimodal posterior samplings from \thejoker.
\textit{Bottom left:}
\textit{Bottom Right:}
\label{fig:logg-teff-p-e}
}
\end{figure}

@@

Most of the companions we find have minimum masses $M_{2, \textrm{min}} <
1~\msun$.
\figurename~\ref{fig:mass}, left panel shows primary and companion mass
estimates for systems with unimodal (black markers) and bimodal (blue lines)
period samplings for the subset of /\nunimodal\ unimodal and /\nbimodal\ bimodal
systems with primary mass estimates, again using primary masses from
\citet{Ness:2015}.
Upper dashed line shows the $M_{2, \textrm{min}} = M_1$ curve, and lower dashed
line shows the Hydrogen-burning limit, $M_{2, \textrm{min}} = 0.08~\msun$.
For the systems with bimodal samplings, we compute the minimum companion mass
for each period mode and connect these estimates with a line.
Here we restrict to stars with $\logg > 2$ to avoid upper RGB stars that may
have surface oscillations that mimic RV modulations from companions.
